The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-01 paper/ms.tex
mike updates

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars that saturated the detector are important because they can be and have been observed very accurately by other instruments. By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars. The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function. We test a range of such objective functions, finding that \textit{lagged Total Variation}, a generalization of Total Variation, performs well on both saturated and unsaturated \ktwo targets. Applying this to the bright stars across the \ktwo Campaigns reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. We describe our pipeline and present a catalogue of the \textcolor{red}{N} bright stars, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}

@@

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected. These parameters are listed in Table~\ref{rgs}. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.

@@

% RGs, Classical pulsators 
\subsection{Pulsators with Self-Driven Modes}
\label{sec:variables}

Our dataset includes a rich variety of classical pulsators. We used visual inspection of the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes such as $\delta$ Scuti stars, $\gamma$ Doradus stars, slowly pulsating B~stars, $\beta$ Cephei pulsators, as well as supergiants showing stochastic variability \citep[][]{Aerts2018,bowman19}. The classes we have determined for each star are listed in Table~\ref{table_all}. A detailed frequency analysis of the variability in each star will be presented in a forthcoming paper (Greklek-McKeon et al., in prep).

\subsection{Chemically-Peculiar Stars}

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion. With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars that saturated the detector are important because they can be and have been observed very accurately by other instruments. By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. The halo method does not depend on the detailed cause and form of systematics, and we show that it is effective at extracting light curves from both normal and saturated stars. The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function. We test a range of such objective functions, finding that \textit{lagged Total Variation}, a generalization of Total Variation, performs well on both saturated and unsaturated \ktwo targets. Applying this to the bright stars across the \ktwo Campaigns reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. We describe our pipeline and present a catalogue of the 161 bright stars, with classifications of their variability, asterosesmic parameters for giants with well-measured solar-like oscillations, and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}

@@

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 giants for which oscillations are detected with sufficient signal-to-noise. These parameters are listed in Table~\ref{rgs}; the stars are noted as showing `RG' variability in Table~\ref{table_all}, whereas this field is left blank for stars of luminosity class III for which oscillations are not unambiguously detected. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.

@@

\subsection{Eclipsing Binaries}
\label{sec:ebs}

We have detected two eclipsing binaries in our sample: the previously-known EB HR\,6773 and the new detection 98\,Tau.

%  HR 6773  is an SPB EB

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98\,Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion. With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.

% RGs, Classical pulsators 
\subsection{Other Variables}
\label{sec:variables}

Our dataset includes a rich variety of classical pulsators. We used visual inspection of the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes. We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, 3~Cepheids, as well as 3~O\,stars 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}. In addition to this, eight stars rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn spot modulation. The classes we have determined for each star are listed in Table~\ref{table_all}. A detailed frequency analysis of the variability in each star will be presented in a forthcoming paper.
